Privacy Analysis of a Mobile Sensor Application

### 2015-01-19 paper.tex
removed legend from fig1, scaled fig1 and fig4 down to 60% textwidth

%input{./figures/IT-Systems}
\begin{figure}[h]
\centering
\includegraphics[width=0.7\textwidth]{diagrams/png/it-systems.png}

\begin{flushleft}
\scriptsize
\textbf{Legend:}
\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt

\item
\textbf{(a) Citizen:} 
User of the L+G client application whose privacy is at stake.

\item
\textbf{(b) Service Provider:} Provides technical infrastructure.

\item
\textbf{(c) Local Authority:} Provider of the L+G system.

\item
\textbf{(d) Mobile Device:}
Runs the L+G client application, produces and stores data sensitive to the users privacy.

\item
\textbf{(e) Data Center:} Runs the L+G services, processes and stores user data.

\item
\textbf{(f) Report Tool:} Interface to aggregated user data.

\end{itemize}
\end{flushleft}

@@

%input{./figures/LG-Vulnerabilities}
\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{diagrams/png/vulnerabilities.png}

>>>>

%input{./figures/IT-Systems}
\begin{figure}[h]
\centering
\includegraphics[width=0.6\textwidth]{diagrams/png/it-systems.png}

%\begin{flushleft}
%\scriptsize
%\textbf{Legend:}
%\begin{itemize}
%\itemsep1pt\parskip0pt\parsep0pt
%
%\item
%\textbf{(a) Citizen:} 
%User of the L+G client application whose privacy is at stake.
%
%\item
%\textbf{(b) Service Provider:} Provides technical infrastructure.
%
%\item
%\textbf{(c) Local Authority:} Provider of the L+G system.
%
%\item
%\textbf{(d) Mobile Device:}
%Runs the L+G client application, produces and stores data sensitive to the users privacy.
%
%\item
%\textbf{(e) Data Center:} Runs the L+G services, processes and stores user data.
%
%\item
%\textbf{(f) Report Tool:} Interface to aggregated user data.
%
%\end{itemize}
%\end{flushleft}

@@

%input{./figures/LG-Vulnerabilities}
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{diagrams/png/vulnerabilities.png}
